### 2017-09-08 paper/related.tex
pass on related work

\textit{Continuous integration services:}
Recent work showed us that Continuous Integration Services are widely
used and improve the productivity~\cite{hilton-etal-ase2016}.

>>>>

Continuous Integration Services are widely used by the open-source
community~\cite{hilton-etal-ase2016,vasilescu-etal-fse2015}. Travis
CI~\cite{travis} is an example of one of these services. Recent work
by Hilton~\etal{}~\cite{hilton-etal-ase2016} showed that there is a
high acceptance rate for CI services. The average build time for those
projects using CI is under $\sim$8.3 min~\cite{hilton-etal-ase2016}.
